Thesis Title

### 2022-03-20 chapters/chapter_2.tex
Updates from Overleaf

As mentioned in \ref{sssec:shotgun_metagenomics}, shotgun metagenomic (SMg) approaches have been a growing interest to deliver clinically relevant results without \textit{a priori} knowledge of what to expect from a particular clinical sample or patient. 
The capacity to detect all potential pathogens in a sample has great potential utility in the diagnosis of infectious disease. 
However, it is unclear how the variety of available methods impacts the end results.

>>>>

As mentioned in Chapter \ref{sssec:shotgun_metagenomics}, shotgun metagenomic (SMg) approaches have been a growing interest to deliver clinically relevant results without \textit{a priori} knowledge of what to expect from a particular clinical sample or patient. 
The capacity to detect all potential pathogens in a sample has great potential utility in the diagnosis of infectious disease. 
However, it is unclear how the variety of available methods impacts the end results.
